Supplementary Information for:

### 2017-07-12 supp/supp.Rmd
fix title, add link to Rmd

---
title: "Supplementary Information for:"
subtitle: A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 1
bibliography: library.bib
---

@@

This supplement provides justification and derivations from the literature for all parameter values used in the model, as well as additional figures that demonstrate the structure and behavior of the model and its specific components.

>>>>

---
title: "Supplementary Information for:"
subtitle: A dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 1
bibliography: library.bib
---

@@

This supplement provides justification and derivations from the literature for all parameter values used in the model, as well as additional figures that demonstrate the structure and behavior of the model and its specific components. R code for each chunk of output in this document can be shown and hidden using the right-aligned "Code" buttons, or for the entire document using the button at the top. This HTML output was knit from an RMarkdown document that can be found [here](https://github.com/jrcunning/coRal-analysis/blob/master/supp/supp.Rmd).
